`r paste(params$species)` climatic and biotic velocities for `r paste(params$region)` (immature: `r paste(params$immature)`

### 2020-02-07 analysis/VOCC/3-vocc-temp.Rmd
rename vocc rendering

---
title: "`r paste(params$species)` climatic and biotic velocities for `r paste(params$region)` (immature: `r paste(params$immature)`"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document 
params: 
    species: "Arrowtooth Flounder" 
    immature: FALSE
    #region: "both odd year surveys"
    #region: "West Coast Haida Gwaii"
    region: "West Coast Vancouver Island"
    covs: "-tv-depth-only"
    scrambled_years: FALSE
---

@@

if (multiyear) {
  # unique(d_all$year)
  d <- d_all %>% filter(ssid %in% model_ssid)
  length(unique(d$year))
  years_sampled <- length(unique(d$year))
  year_range <- (years_sampled - 1) * 2

@@

glimpse (d)
if (scrambled_years) {
  d2 <- list()
  # set.seed(9999) 
  # set.seed(12345)
  # set.seed(98765) 
  original_years <- unique(d$year)
  new_years <- sample(original_years, replace=F)
  convert <- cbind(original_years, new_years)
  convert
  for (i in seq_len(length(original_years))) {
    old_year <- as.integer(convert[[i,1]])
    fake_year <- as.integer(convert[[i,2]])
    d2[[i]] <- filter(d, year == old_year) %>% 
      mutate(year = fake_year )
     # browser()
  }
  d <- do.call(rbind, d2)
  convert
}
```

@@

d <- left_join(d, nd_all, by = c("X", "Y", "year"))
d <- left_join(d, fishing, by = c("X", "Y", "year"))
d$log_effort[is.na(d$log_effort)] <- -2.3
d$effort[is.na(d$effort)] <- 0

@@

gf <- gf %>%
  mutate(
    fishing_trend = trend,
    mean_effort = exp(mean)
  ) %>%
  dplyr::mutate(X = x, Y = y) %>%
  gfplot:::utm2ll(., utm_zone = 9)

effort <- plot_vocc(gf,
  # theme_black = TRUE,
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  #NA_label = "NA",
  fill_col = "mean_effort",
  fill_label = "mean effort",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
   na_colour = "white",
  # high_fill = "Steel Blue 4",
  # low_fill = "Red 3",
  # white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = fourth_root_power#
) + labs(
  title = "Fishing presssure",
  subtitle = paste0(min(d$year), "-", max(d$year))
)

@@

gf2$gradient_diff <- gf2$gradient - gf2$grad_all
range(gf2$gradient_diff)

grad2 <- plot_vocc(gf2,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "velocity",# "velo_t2_grad", # "trend", #"gradient_diff", 
  fill_label = "velocity", #"trend",
  raster_alpha = 1,
  # raster_limits = c(-6, 6),
  # raster_limits = c(raster_min, raster_max),
  na_colour = "black",
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = fourth_root_power # sqrt #no_trans # log10 # 
) + labs(
  title = "temp velocity",
  subtitle = paste0(min(d$year), "-", max(d$year))
)

@@

gf3 <- gf3 %>%
  mutate(
    CV_formula = sqrt(exp(cv^2) - 1),
    CV = sd / exp(mean),
    mean_biomass = exp(mean) * 10000,
    #trend_per_year = exp(trend),
    #trend_per_decade = trend_per_year * 10,
    velocity = velocity
  ) %>%
  dplyr::mutate(X = x, Y = y)

@@

```{r}

grad4 <- gfranges::plot_vocc(gf3t,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "mean_biomass",
  fill_label = "mean",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "black",
  # white_zero = TRUE,
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
  title = paste0(species, " (", age, ")"), #
  subtitle = paste0("Mean biomass ", min(d$year), "-", max(d$year))
)
grad4
```

```{r}
grad5 <- gfranges::plot_vocc(gf3t,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "trend",
  fill_label = "biomass trend",
  raster_alpha = 1,
  # raster_limits = c(0, 10),
  na_colour = "black",
  white_zero = TRUE,
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
  title = paste0(species, " (", age, ")"), #
  subtitle = paste0("Biomass trend ", min(d$year), "-", max(d$year))
)
grad5
```

```{r}
grad6 <- gfranges::plot_vocc(gf3t,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "cv",
  fill_label = "sd in log space",
  raster_alpha = 1,
  # raster_limits = c(0, 7),
  na_colour = "black",
  # white_zero = TRUE,
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
  title = paste0(species, " (", age, ")"), #
  subtitle = paste0("Biotic variability (cv from vocc_gradient_calc funcition) ", min(d$year), "-", max(d$year))
)
grad6
```

```{r}
raster_max <- quantile(gf3t$CV, 0.90, na.rm = TRUE)
grad7 <- gfranges::plot_vocc(gf3t,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "CV",
  fill_label = "CV",
  raster_alpha = 1,
  raster_limits = c(0, raster_max),
  na_colour = "black",
  # white_zero = TRUE,
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
  title = paste0(species, " (", age, ")"), #
  subtitle = paste0("CV in estimated biomass ", min(d$year), "-", max(d$year))
)
grad7
```

### Save gradient-based VOCCs
```{r}

biotic_values <- gf3t %>%
  rename(
    biotic_vel = velocity,
    biotic_trend = trend,
    biotic_CV = CV,
    sd_est = cv,
    biotic_grad = gradient
  ) %>%
  mutate(
    sd_biomass = sd * 10000,
    mean_biomass = exp(mean) * 10000
  ) %>%
  select(x, y, biotic_vel, biotic_trend, biotic_grad, biotic_CV, sd_est, sd_biomass, mean_biomass) %>%
  mutate(start_year = !!start_year)

@@

vocc <- left_join(biotic_values, fished) # add fishing effort
# vocc <- left_join(vocc, DO_values) # add DO
vocc <- left_join(vocc, temp_values) # add temp
vocc <- mutate(vocc, species = !!species, method = "gradient")

write.csv(vocc, file = paste0(
  "data/_all_temp/", age,  "-all-temp-vocc-", spp, "-", ssid_string, "-", covs, "-", min(d$year), "-", max(d$year), "-trim10.csv"
))
```

>>>>

---
title: "`r paste(params$species)` climatic and biotic velocities for `r paste(params$region)` (immature: `r paste(params$immature)`"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document 
params: 
    #species: "Arrowtooth Flounder" 
    species: "Yelloweye Rockfish"
    immature: FALSE
    region: "both odd year surveys"
    #region: "West Coast Haida Gwaii"
    #region: "West Coast Vancouver Island"
    covs: "-tv-depth-only"
    #scrambled_years: FALSE
---

@@

if (multiyear) {
  # unique(d_all$year)
  d <- d_all %>% filter(ssid %in% model_ssid) %>% filter(year >= start_year)
  length(unique(d$year))
  years_sampled <- length(unique(d$year))
  year_range <- (years_sampled - 1) * 2

@@

glimpse (d)
# 
# if (scrambled_years) {
#   d2 <- list()
#   # set.seed(9999) 
#   # set.seed(12345)
#   # set.seed(98765) 
#   original_years <- unique(d$year)
#   new_years <- sample(original_years, replace=F)
#   convert <- cbind(original_years, new_years)
#   convert
#   for (i in seq_len(length(original_years))) {
#     old_year <- as.integer(convert[[i,1]])
#     fake_year <- as.integer(convert[[i,2]])
#     d2[[i]] <- filter(d, year == old_year) %>% 
#       mutate(year = fake_year )
#      # browser()
#   }
#   d <- do.call(rbind, d2)
#   convert
# }
```

@@

d <- left_join(d, nd_all, by = c("X", "Y", "year"))
d <- left_join(d, fishing, by = c("X", "Y", "year"))
d$effort[is.na(d$effort)] <- 0
d$log_effort[is.na(d$log_effort)] <- -2.3

@@

gf <- gf %>%
  mutate(
    fishing_trend = trend,
    mean_effort = exp(mean) # gives geometric mean
  ) %>%
  dplyr::mutate(X = x, Y = y) %>%
  gfplot:::utm2ll(., utm_zone = 9)
```

```{r eval = FALSE }
effort <- plot_vocc(gf,
  # theme_black = TRUE,
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  #NA_label = "NA",
  fill_col = "mean_effort",
  fill_label = "mean effort",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
   na_colour = "white",
  # high_fill = "Steel Blue 4",
  # low_fill = "Red 3",
  # white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = fourth_root_power#
) + labs(
  title = "Fishing presssure",
  subtitle = paste0(min(d$year), "-", max(d$year))
)

@@

gf2$gradient_diff <- gf2$gradient - gf2$grad_all
range(gf2$gradient_diff)
```

```{r eval = FALSE}
grad2 <- plot_vocc(gf2,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "velocity",# "velo_t2_grad", # "trend", #"gradient_diff", 
  fill_label = "velocity", #"trend",
  raster_alpha = 1,
  # raster_limits = c(-6, 6),
  # raster_limits = c(raster_min, raster_max),
  na_colour = "black",
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = fourth_root_power # sqrt #no_trans # log10 # 
) + labs(
  title = "temp velocity",
  subtitle = paste0(min(d$year), "-", max(d$year))
)

@@

gf3 <- gf3 %>%
  mutate(
    CV_formula = sqrt(exp(cv^2) - 1),
    CV = sd / exp(mean),
    mean_biomass = exp(mean) * 10000,
    #trend_per_year = exp(trend),
    #trend_per_decade = trend_per_year * 10,
    velocity = velocity
  ) %>%
  dplyr::mutate(X = x, Y = y)
```

```{r eval = FALSE}

@@

```{r eval = FALSE}
grad4 <- gfranges::plot_vocc(gf3t,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "mean_biomass",
  fill_label = "mean",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "black",
  # white_zero = TRUE,
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
  title = paste0(species, " (", age, ")"), #
  subtitle = paste0("Mean biomass ", min(d$year), "-", max(d$year))
)
grad4
```

```{r eval = FALSE}
grad5 <- gfranges::plot_vocc(gf3t,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "trend",
  fill_label = "biomass trend",
  raster_alpha = 1,
  # raster_limits = c(0, 10),
  na_colour = "black",
  white_zero = TRUE,
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
  title = paste0(species, " (", age, ")"), #
  subtitle = paste0("Biomass trend ", min(d$year), "-", max(d$year))
)
grad5
```

```{r eval = FALSE}
grad6 <- gfranges::plot_vocc(gf3t,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "cv",
  fill_label = "sd in log space",
  raster_alpha = 1,
  # raster_limits = c(0, 7),
  na_colour = "black",
  # white_zero = TRUE,
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
  title = paste0(species, " (", age, ")"), #
  subtitle = paste0("Biotic variability (cv from vocc_gradient_calc funcition) ", min(d$year), "-", max(d$year))
)
grad6
```

```{r eval = FALSE}
raster_max <- quantile(gf3t$CV, 0.90, na.rm = TRUE)
grad7 <- gfranges::plot_vocc(gf3t,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "CV",
  fill_label = "CV",
  raster_alpha = 1,
  raster_limits = c(0, raster_max),
  na_colour = "black",
  # white_zero = TRUE,
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
  title = paste0(species, " (", age, ")"), #
  subtitle = paste0("CV in estimated biomass ", min(d$year), "-", max(d$year))
)
grad7
```

### Save gradient-based VOCCs
```{r}
biotic_values <- gf3 %>%
  rename(
    biotic_vel = velocity,
    biotic_trend = trend,
    biotic_CV = CV,
    sd_est = cv,
    biotic_grad = gradient
  ) %>%
  mutate(
    sd_biomass = sd * 10000,
    mean_biomass = exp(mean) * 10000
  ) %>%
  select(x, y, biotic_vel, biotic_trend, biotic_grad, biotic_CV, sd_est, sd_biomass, mean_biomass) %>%
  mutate(start_year = !!start_year)

@@

vocc <- left_join(biotic_values, fished) # add fishing effort
# vocc <- left_join(vocc, DO_values) # add DO
vocc <- left_join(vocc, temp_values) # add temp
vocc <- mutate(vocc, species = !!species, method = "gradient")
vocc$ssid <- ssid_string
```

```{r}
# glimpse(vocc)
```

```{r}
write.csv(vocc, file = paste0(
  "data/_new_null/", age,  "-all-temp-nulls-", spp, "-", ssid_string, "-", covs, "-", min(d$year), "-", max(d$year), ".csv"
))
```
